\input{preamble}

\title{Section 6.1 --- Coordinate Geometry}

\begin{document}
\maketitle

\section*{Practice With Points}
\begin{senum}
\item On a separate sheet of graph paper (or the other side of this sheet), draw appropriate axes and:
\begin{enumerate}
\item Plot the points $A=(-4,3)$ and $B=(2,-5)$, and sketch $\overline{AB}$.
\item Plot a point $C$ so that $\triangle ABC$ is a right triangle with legs parallel to the $x$- and $y$-axes.
\item What are the coordinates of the point $C$?
\item Find length $AC$ by looking at the graph.
\item Find length $BC$ by looking at the graph.
\item Find length $AB$ using the Pythagorean Theorem (without using the distance formula).
\item Plot the midpoint $M$ of $AB$ visually. What are the coordinates of $M$?
\end{enumerate}
\end{senum}

\section*{Distance Formula}
Using the distance formula (without plotting on a graph) find the distance between the two points given. If necessary, give your answer as a simplified radical and as a decimal approximation.
\begin{smenum}
\mitemxxx
{$(-3,5)$ and $(9,10)$}
{$(4,2)$ and $(7,6)$}
{$(-8,-1)$ and $(-6,-2)$}
\mitemxxx
{$(3.4,1.7)$ and $(5.4,-0.4)$}
{$\left(0,\frac{24}{25}\right)$ and $\left(\frac{7}{25},0\right)$}
{$(3,5)$ and $\left(\frac{7}{3},\frac{11}{9}\right)$}
\end{smenum}

\section*{Midpoint Formula}
For each pair of points $A$ and $B$ given below, find the midpoint of $\overline{AB}$.
\begin{smenum}
\mitemxxx
{$A=(-2,5)$, $B=(6,-1)$}
{$A=(5,7)$, $B=(11,2)$}
{$A=(-6,-2)$, $B=(-11,-6)$}
\mitemxxx
{$A=\left(\frac{3}{2},\frac{7}{3}\right)$, $B=\left(\frac{7}{2},\frac{11}{3}\right)$}
{$A=(0.3,1.7)$, $B=(2.3,5.7)$}
{$A=(-7,11)$, $B=(-70,110)$}
\end{smenum}

\section*{Triangles and Inequalities}
For each list of three values, classify them as one of the following.
\begin{Clist}
\item Not possible as the distances between three points.
\item Distances between three collinear points.
\item Side lengths of an obtuse triangle.
\item Side lengths of a right triangle.
\item Side lengths of an acute triangle.
\end{Clist}
\begin{smenum}
\mitemxxxxx
{9, 17, 9}
{17, 8, 9}
{6, 5, 7}
{10, 22, 10}
{8, 15, 17}
\mitemxxxxx
{6, 5, 11}
{8, 9, 6}
{9, 12, 5}
{16, 5, 5}
{13, 5, 12}
\end{smenum}

\section*{Classifying Triangles}
Use the distance formula to classify each set of three points as:
\begin{Clist}
\item Three collinear points
\item Corners of an obtuse triangle
\item Corners of a right triangle
\item Corners of an acute triangle
\end{Clist}
\begin{smenum}
\mitemxx
{$A=(-3,5)$, $B=(0,3)$, $C=(6,-1)$}
{$A=(2,4)$, $B=(5,2)$, $C=(1,-4)$}
\mitemxx
{$A=(-5,-10)$, $B=(-1,-8)$, $C=(1,-6)$}
{$A=(-4,5)$, $B=(4,6)$, $C=(1,2)$}
\end{smenum}
\graphpage
\end{document}