\input{preamble}

\title{Section 4.6 --- Euler's Number}

\begin{document}
\maketitle

\section{Euler's Number and the Natural Log}
Compute each of the following by hand, using the definition of the natural log.
\begin{smenum}
\mitemxxxxx
{$\ln e^3$}
{$\ln e$}
{$\ln\left(\frac{1}{e}\right)$}
{$\ln\sqrt{e}$}
{$\ln e^{0.13}$}
\end{smenum}
Compute each of the following on your calculator. Round your answer to three decimal places.
\begin{smenum}
\mitemxxxxx
{$e^3$}
{$e^1$}
{$e^{1/2}$}
{$e^{-5}$}
{$e^{0.07}$}
\mitemxxxxx
{$\ln 4$}
{$\ln 1.6$}
{$\ln\left(\frac{1}{2}\right)$}
{$\ln 0.01$}
{$\ln 1.01$}
\end{smenum}

\section{Interest Compounded Continuously}
You may wish to reference the formulas for compound interest and interest compounded continuously in solving these problems and the ones in the next section.
$$P(t)=P_0\left(1+\frac{r}{n}\right)^{nt}
\qquad
P(t)=P_0e^{rt}$$
\begin{senum}
\item Andre invests \$700 at an interest rate of 16\%, compounded continuously. What is his investment worth after 5 years? Round to the nearest cent.
\item Beatrice will borrow some money at 4.8\% interest, compounded continuously. She will repay \$1200 at the end of 10 years. How much can she borrow? (Round so that she will not have to repay more than \$1200.)
\item Carlos borrows \$900, and pays back \$1100 after 3 years. What interest rate does this represent, if it's compounded continuously? Answer as a percent, rounded to one decimal place.
\item Danielle invests \$500 at an interest rate of 7\%, compounded continuously. How long must she wait for her investment to be worth \$1200? Round to two decimal places.
\item Ernie is considering an investment which promises 6\% interest, compounded continuously. What is the doubling time on this investment? Round to two decimal places.
\end{senum}

\section{Equivalent Interest Rates}
For each loan below, find the equivalent interest rate if the loan were compounded continuously. Answer as a percent, rounded to two decimal places.
\begin{senum}
\item 4\% interest rate, compounded annually
\item 6.7\% interest rate, compounded quarterly
\item 11.2\% interest rate, compounded monthly
\end{senum}
For each loan below, find the equivalent interest rate if the loan were compounded annually. Answer as a percent, rounded to two decimal places.
\begin{senum}
\item 9.3\% interest rate, compounded quarterly
\item 3.6\% interest rate, compounded monthly
\item 7.1\% interest rate, compounded continuously.
\end{senum}
\clearpage
\noindent Answer each of the questions below.
\begin{senum}
\item Francesca is comparing three loan options, with the following interest rates: 6.2\%, compounded annually; 6.15\%, compounded monthly; or 6.12\%, compounded continuously.
\begin{clist}
\item Find the equivalent interest rate for each loan if it were compounded annually.
\item Find the equivalent interest rate for each loan if it were compounded continuously.
\item Assuming all the other terms of the loan are the same, which loan should Francesca choose?
\item Would your answer in part (c) be different if she were considering an investment?
\end{clist}
\item George invests \$1300, and after 15 years his investment is worth \$2900. What interest rate does this represent if we consider the interest to be compounded with each frequency below? Answer as a percent, rounded to two decimal places.
\begin{clist}
\item Annually
\item Quarterly
\item Monthly
\item Continuously
\end{clist}
\end{senum}

\section{Percent Rate of Change}
In the questions below, pay close attention to the tricky wording. (Increases/decreases by some percent each time, vs. increases/decreases at a rate of some percent per time.)
\begin{senum}
\item The population of bacteria in a petri dish increases at a rate of 13\% per hour. If there are 500 bacteria in the petri dish now, how long will it take for the population to reach at least 7000? Answer as a whole number of hours.
\item 22\% of the copies of a certain collectable in circulation are destroyed each year. If 500,000 copies were initially released, how many will remain after 10 years?
\item Each year, a company's profits are 12\% greater than in the previous year. If their profits this year are \$12 million, what will their profits be three years from now? Round your answer to the nearest million.
\item The amount of a drug in a patient's body decreases at a rate of 6\% per hour. If a 100mg dose is initially administered, how much will remain after 24 hours? Round your answer to the nearest whole milligram (mg).
\end{senum}

\end{document}