\input{preamble}

\title{Section 3.10 --- Simplifying Radical Expressions}

\begin{document}
\maketitle

\section{Simplifying Radical Expressions}
Simplify each expression. Do \emph{not} assume variables represent positive real numbers.
\begin{smenum}
\mitemxxxx
{$\sqrt{96}$}
{$\sqrt[3]{32}$}
{$\sqrt[5]{128}$}
{$\sqrt[4]{3888}$}
\mitemxxxx
{$\sqrt{x^6y^8z^{10}}$}
{$\sqrt{r^9x^5}$}
{$\sqrt[3]{m^{13}n^9}$}
{$\sqrt[4]{243x^9}$}
\mitemxxxo
{$\sqrt[5]{160n^{18}}$}
{$\sqrt[3]{486x^{16}}$}
{$\sqrt[7]{a^{16}b^9c^{12}}$}
\end{smenum}

\section{Rationalizing Denominators}
Rationalize each denominator. Assume all variables represent positive real numbers.
\begin{smenum}
\mitemxxx
{$\dfrac{4}{\sqrt{2x^3}}$}
{$\sqrt[3]{\dfrac{8x^4}{9y}}$}
{$\sqrt{\dfrac{12x}{5y^5}}$}
\end{smenum}
Rationalize each denominator. Write your answer as a fraction with a positive integer denominator. (If necessary, multiply your numerator and denominator by $-1$.)
\begin{smenum}
\mitemxxx
{$\dfrac{5}{1-\sqrt{3}}$}
{$\dfrac{8+\sqrt{6}}{5+\sqrt{6}}$}
{$\dfrac{3}{2-\sqrt{2}}$}
\mitemxxx
{$\dfrac{7}{\sqrt{2}+\sqrt{6}}$}
{$\dfrac{2+\sqrt{5}}{1+2\sqrt{3}}$}
{$\dfrac{4}{\sqrt{5}-\sqrt{2}}$}
\end{smenum}

\section{Multiple Radical Terms}
Add or subtract.  Simplify your answer as much as possible. Assume all variables represent positive real numbers.
\begin{smenum}
\mitemxxxx
{$5\sqrt{y}+7\sqrt{y}$}
{$\sqrt{80y^3}-y\sqrt{125y}$}
{$\sqrt[3]{24}+\sqrt[3]{81}$}
{$\dfrac{2}{\sqrt[4]{8}}+5\sqrt[4]{2}$}
\mitemxx
{$12n\sqrt[3]{2n}-14m\sqrt[3]{5m}-8n\sqrt[3]{2n}+18m\sqrt[3]{5m}$}
{$3\sqrt{180}-\sqrt{192}+4\sqrt{\frac{16}{5}}-\sqrt{48}$}
\end{smenum}

\section{Write as a Single Radical}
Use rational exponents to simplify each expression by writing it as a single simplified radical.  Assume all variables represent positive real numbers.
\begin{smenum}
\mitemxxxx
{$\sqrt[4]{y}\sqrt[3]{y^2}$}
{$\sqrt[5]{x^4}\sqrt{x}$}
{$\dfrac{\sqrt[3]{y^5}}{\sqrt[4]{y^3}}$}
{$\sqrt[4]{6}\sqrt[3]{2}$}
\mitemxxxx
{$\sqrt{\sqrt[3]{n}}$}
{$\sqrt[3]{x\sqrt[3]{x^2}}$}
{$\sqrt{2\sqrt[3]{6}}$}
{$\sqrt[4]{\sqrt[5]{96}}$}
\end{smenum}

\section{Roots in Lowest Terms}
Simplify by writing each expression with the smallest possible index. Assume all variables represent positive real numbers. Give your answer as a simplified radical.
\begin{smenum}
\mitemxxxx
{$\sqrt[6]{x^3}$}
{$\sqrt[8]{z^6}$}
{$\sqrt[9]{y^{12}}$}
{$\sqrt[4]{w^{10}}$}
\mitemxxxx
{$\sqrt[4]{49}$}
{$\sqrt[6]{125}$}
{$\sqrt[4]{64}$}
{$\sqrt[9]{-27}$}
\end{smenum}

\end{document}