\input{preamble}

\newcommand{\expans}[4]{\begin{nmenum}\mitemxxx{Base:\hfill$#1$,\quad Exponent:\quad$#2$\quad\quad}{$#3$}{$#4$}\end{nmenum}}

\newcommand{\polyfacts}[4]{\begin{nmenum}\mitemxoxx
{Leading term: $#1$, Ldg. Coefficient: $#2$}
{Degree: #3}
{#4}\end{nmenum}}

\title{Section 2.1 --- Monomials and Polynomials --- Answer Key}

\begin{document}
\maketitle
\section{Exponents}
For each expression below:
\begin{clist}
\item Identify the base and the exponent.
\item Rewrite as repeated multiplication.
\item Evaluate by multiplying, then check your answer using the exponent key on your calculator.
\end{clist}
\begin{senum}
\item\expans{2}{3}{2\cdot 2\cdot 2}{8}
\item\expans{3}{4}{3\cdot 3\cdot 3\cdot 3}{81}
\item\expans{-4}{2}{(-4)(-4)}{16}
\item\expans{5}{3}{5\cdot 5\cdot 5}{125}
\item\expans{-1}{5}{(-1)(-1)(-1)(-1)(-1)}{-1}
\end{senum}
For each of the expressions below:
\begin{clist}
\item Rewrite using a positive exponent.
\item Evaluate using your rewritten expression, then check your answer using your calculator. Answer as a fraction.
\end{clist}
\begin{smenum}
\mitemxxxxx
{$\dfrac{1}{3^2}=\dfrac{1}{9}$}
{$\dfrac{1}{5^1}=\dfrac{1}{5}$}
{$\left(\dfrac{3}{2}\right)^3=\dfrac{27}{8}$}
{$\dfrac{1}{(-4)^3}=-\dfrac{1}{64}$}
{$\left(-\dfrac{1}{3}\right)^4=\dfrac{1}{81}$}
\end{smenum}

\section{Simplifying Monomials}
Simplify each monomial below, applying exponent rules as appropriate.
\begin{smenum}
\mitemxxxx
{$b^5$}
{$10y^5z$}
{$9x^6$}
{$\frac{81}{16}x^4$}
\mitemxxxo
{$64x^{14}y^2$}
{$\frac{1}{6}x^3y^3$}
{$-84h^3j^5k^2y$}
\end{smenum}

\section{Using Polynomial Vocabulary}
For each expression, decide whether it is
\begin{Nmenum}
\mitemxxx
{not a polynomial\mlbl{not}}
{a monomial\mlbl{monom}}
{a binomial\mlbl{binom}}
\mitemxxo
{a trinomial\mlbl{trinom}}
{a polynomial with 4 or more terms\mlbl{more}}
\end{Nmenum}
\begin{smenum}
\mitemxxxx
{C}
{B}
{B}
{D}
\mitemxxxx
{B}
{B}
{A}
{A}
\mitemxxxx
{B}
{B}
{E}
{A}
\mitemxxxx
{B}
{B}
{A}
{C}
\end{smenum}
\clearpage
For each polynomial below:
\begin{clist}
\item Identify the leading term and leading coefficient, if any.
\item Give the degree of the polynomial.
\item Identify any that are constant, linear, quadratic, or cubic.
\end{clist}
\begin{senum}
\item\polyfacts{N/A}{N/A}{1}{Linear}
\item\polyfacts{17.3x}{17.3}{2}{Quadratic}
\item\polyfacts{18xy^3}{18}{4}{None of these}
\item\polyfacts{x^3}{1}{3}{Cubic}
\item\polyfacts{7k}{7}{1}{Linear}
\item\polyfacts{36}{36}{0}{Constant}
\item\polyfacts{-x^2}{-1}{2}{Quadratic}
\item\polyfacts{-u^7}{-1}{7}{None of these}
\end{senum}
%\begin{smenum}
%\mitemxxxx
%{$6x+8y+3z$}
%{$17.3x^2-3x+2.1$}
%{$18xy^3$}
%{$x^3-4x^2+4x+4$}
%\mitemxxxx
%{$7k+5$}
%{$36$}
%{$25-x^2$}
%{$2u^2+5u^3-u^7$}
%\end{smenum}
%
Give an example of each of the following.\\\textbf{Answers will vary; these are possible examples.}
\begin{senum}
\item $3x^2-5x+2$
\item $x^3+x^2y+xy^2+y^3$
\item $2x-5$
\item $x^3+8$
\end{senum}

\section{Polynomial Functions}
Let $f(n)=n^2-8n-3$.  Find:
\begin{smenum}
\mitemxxxx
{$f(2)=-15$}
{$f(-3)=30$}
{$f(\frac{1}{2})=-\frac{27}{4}$}
{$f(0)=-3$}
\end{smenum}
Let $g(j)=22j^3+5j^2-16j^4+21-14j$.  Find:
\begin{smenum}
\mitemxxxx
{$g(1)=18$}
{$g(-2)=-363$}
{$g(\frac{1}{4})=579/32$}
{$g(-1)=2$}
\end{smenum}

\end{document}