\input{preamble}

\title{Section 2.9 --- Arithmetic of Rational Expressions --- Answer Key}

\begin{document}
\maketitle
\section{Multiplying Rational Expressions}
Multiply.  Simplify your answer as much as possible.  You may leave your answer in factored form.
\begin{smenum}
\mitemxxx
{$\dfrac{3x^2}{2y^2}$}
{$\dfrac{1}{a^2by}$}
{$1$}
\mitemxxo
{$\dfrac{(x-2)(x-5)(x+3)}{x}$}
{$\dfrac{q+5}{q+4}$}
\end{smenum}

\section{Dividing Rational Expressions}
Dividing.  Simplify your answer as much as possible.  You may leave your answer in factored form.
\begin{smenum}
\mitemxx
{$\dfrac{1}{a^3b}$}
{$\dfrac{32a^7}{45x}$}
\mitemxx
{$\dfrac{(x-8)(x+2)(9x^2+12x+16)}{(x-2)(x+8)(2x-3)}$}
{$\dfrac{1}{(u-1)(u-3)}$}
\end{smenum}

\section{Least Common Multiple of Monomials}
Find the least common multiple of each list of monomials.  (The comma separates items on a list.)
\begin{smenum}
\mitemxxx
{$rt$}
{$27m^3n^3$}
{$8x^3y^3z^5$}
\end{smenum}

\section{Least Common Multiple of Polynomials}
Find the least common multiple of each list of polynomials.  (The comma separates items on a list.)  Give your answer in factored form.
\begin{smenum}
\mitemxxx
{$(y+2)(y-2)$}
{$24(x-2)$}
{$7(y-3)^3$}
\mitemxxx
{$(b-7)(b+5)(b+2)$}
{$(y-3)(y+5)$}
{$z(z-2)(z+2)(z^2+2z+4)$}
\end{smenum}

\section{Adding and Subtracting Rational Expressions}
Add or subtract, as indicated.  Simplify your answer as much as possible.  You may leave your answer in factored form.
\begin{smenum}
\mitemxxx
{$\dfrac{3x^2}{z}$}
{$\dfrac{18x^2+10y^2}{5xy}$}
{$\dfrac{8}{3c}$}
\mitemxxx
{$\dfrac{5a-3ab}{b^2}$}
{$\dfrac{8}{x+1}$}
{$\dfrac{1}{x+4}$}
\mitemxxx
{$\dfrac{8y-2}{(y+2)(y-4)}$}
{$\dfrac{-3}{t-3}$}
{$\dfrac{z^2+7z+13}{(z+4)(x-3)}$}
\mitemxxx
{$\dfrac{x+1}{x(x+4)}$}
{$\dfrac{t^2-27t+36}{(t-3)(t+3)(t-5)}$}
{$\dfrac{3w-5}{(w-5)(w+1)(w+2)}$}
\end{smenum}

\section{Mixed Operations}
Perform the indicated operations.  Be sure to obey the order of operations.  Simplify your answer as much as possible.
\begin{smenum}
\mitemxx
{$\dfrac{11x+27}{3x(x+3)}$}
{$\dfrac{8x^2+2y^2}{(2x-y)^2}$}
\end{smenum}


\end{document}