\input{preamble}

\title{Section 2.9 --- Arithmetic of Rational Expressions}

\begin{document}
\maketitle
\section*{Multiplying Rational Expressions}
Multiply.  Simplify your answer as much as possible.  You may leave your answer in factored form.
\begin{smenum}
\mitemxxxo
{$\dfrac{x}{y}\cdot\dfrac{3x}{2y}$}
{$\dfrac{ab}{xy}\cdot\dfrac{x}{a^3b^2}$}
{$\dfrac{6x^2+x-12}{2x^2-5x-12}\cdot\dfrac{3x^2-14x+8}{9x^2-18x+8}$}
\mitemxx
{$\dfrac{x^2-7x+10}{x^3-3x^2+9x}\cdot\Gp{x^3+27}$}
{$\dfrac{mn+2m+4n+8}{np-3n+2p-6}\cdot\dfrac{pq+5p-3q-15}{mq+4m+4q+16}$}
\end{smenum}

\section*{Dividing Rational Expressions}
Dividing.  Simplify your answer as much as possible.  You may leave your answer in factored form.
\begin{smenum}
\mitemxx
{$\dfrac{a^3}{b^3}\div\dfrac{a^5}{b^2}$}
{$\dfrac{8x^7g^3}{15x^2g^4}\div\Gp{-\dfrac{3xg^2}{4x^2g^3}}$}
\mitemxx
{$\dfrac{x^2-6x-16}{3x^2-10x+8}\div\dfrac{2x^2+13x-24}{27x^3-64}$}
{$\dfrac{u^2+7u+12}{u^2+u-6}\div\Gp{u^2+u-12}$}
\end{smenum}

\section*{Least Common Multiple of Monomials}
Find the least common multiple of each list of monomials.  (The comma separates items on a list.)
\begin{smenum}
\mitemxxx
{$r \quad,\quad t$}
{$9mn^3 \quad,\quad 27m^3n$}
{$4x^3y \quad,\quad 8x^2y^3z \quad,\quad xy^3z^5$}
\end{smenum}

\section*{Least Common Multiple of Polynomials}
Find the least common multiple of each list of polynomials.  (The comma separates items on a list.)  Give your answer in factored form.
\begin{smenum}
\mitemxx
{$y+2 \quad,\quad y-2$}
{$6x-12 \quad,\quad 8x-16$}
\mitemxx
{$x^2-6x+9 \quad,\quad 7x-21$}
{$b^2-2b-35 \quad,\quad b^2+7b+10$}
\mitemxx
{$y-3 \quad,\quad y^2+2y-15 \quad,\quad y+5$}
{$z^2-4 \quad,\quad z^2-2z \quad,\quad z^3-8$}
\end{smenum}

\section*{Adding and Subtracting Rational Expressions}
Add or subtract, as indicated.  Simplify your answer as much as possible.  You may leave your answer in factored form.
\begin{smenum}
\mitemxxx
{$\dfrac{5x^2}{3z}+\dfrac{4x^2}{3z}$}
{$\dfrac{18x^2}{5xy}+\dfrac{10y^5}{5xy}$}
{$\dfrac{5}{2c}+\dfrac{1}{6c}$}
\mitemxxx
{$\dfrac{5a}{b^2}-\dfrac{3a}{b}$}
{$\dfrac{x^2+2}{x+1}+\dfrac{6-x^2}{x+1}$}
{$\dfrac{v+8}{v^2+8v+16}-\dfrac{4}{v^2+8v+16}$}
\mitemxxx
{$\dfrac{3}{y+2}+\dfrac{5}{y-4}$}
{$\dfrac{3}{t-3}+\dfrac{6}{3-t}$}
{$\dfrac{z+5}{z^2+z-12}+\dfrac{z+2}{z-3}$}
\mitemxxx
{$\dfrac{x-2}{x^2-16}-\dfrac{1}{x^2-4x}$}
{$\dfrac{4t}{t^2-9}-\dfrac{3t-2}{t^2-8t+15}$}
{$\dfrac{w-7}{w^2+4w-5}-\dfrac{w-9}{w^2+3w-10}$}
\end{smenum}

\section*{Mixed Operations}
Perform the indicated operations.  Be sure to obey the order of operations.  Simplify your answer as much as possible.
\begin{smenum}
\mitemxx
{$\dfrac{3}{x}+\dfrac{1}{x^2+3x}\cdot\dfrac{2x}{3}$}
{$\Gp{\dfrac{2x-y}{2x+y}+\dfrac{2x+y}{2x-y}}\div\dfrac{2x-y}{2x+y}$}
\end{smenum}


\end{document}