\input{preamble}

\title{Section 5.4 --- Fundamental Theorem of Algebra --- Answer Key}

\newcommand{\iqf}{irreducible quadratic factor}

\NewDocumentCommand{\ptype}{m m o}{%
a. $D=#1$ - #2\\%
b. \IfNoValueTF{#3}{N/A}{$#3$}%
}
\newcommand{\fac}{Factorable}
\newcommand{\pri}{Prime}
\newcommand{\irr}{Irreducible}
\newcommand{\ifac}[3][x]{\left(#1-(#2+#3)\right)\left(#1-(#2-#3)\right)}
\newcommand{\rfac}[3][x]{\left(#1#2\right)\left(#1#3\right)}

\begin{document}
\maketitle

\section*{Prime or Irreducible}
For each quadratic polynomial below:
\begin{clist}
\item Compute the discriminant. Based on the discriminant, determine whether the polynomial is factorable (with rational coefficients), prime (but not irreducible), or irreducible.
\item If the polynomial is not irreducible, factor using the $ac$ method, completing the square, or the quadratic formula (whichever you prefer).
\end{clist}
\begin{smenum}
\mitemxx
{\ptype{28}{\pri}[\ifac{-1}{\sqrt{7}}]}
{\ptype{-4}{\irr}}
\mitemxx
{\ptype{36}{\fac}[\rfac{-4}{+2}]}
{\ptype{20}{\pri}[\ifac{3}{\sqrt{5}}]}
\mitemxx
{\ptype{4}{\fac}[\rfac{+3}{+1}]}
{\ptype{-36}{\irr}}
\end{smenum}

\section*{Count of Roots}
For each polynomial below, determine the maximum number of real roots it has, up to multiplicity. (Don't try to find any of them.)
\begin{smenum}
\mitemxxxxx
{6}
{7}
{9}
{12}
{11}
\end{smenum}
Determine the number of real roots of each polynomial described below.
\begin{smenum}
\mitemxxx{6}{8}{0}
\end{smenum}
Determine the number of irreducible quadratic factors of each polynomial described below. If this can't happen, write ``impossible.''
\begin{smenum}
\mitemxxx{1}{2}{impossible}
\end{smenum}

\section*{Factoring Fully}
Fully factor each polynomial as a product of linear and irreducible quadratic factors. Some factors may have irrational coefficients.
\begin{smenum}
\mitemx
{$\Gp{4z-5}\Gp{z+6}\ifac{-3}{\sqrt{6}}$}
\mitemx
{$\Gp{t+1}\Gp{2t+1}\Gp{t^2-10t+29}$}
\end{smenum}
Write each polynomial below in factored form, given that it has the irreducible quadratic factor shown.
\begin{smenum}
\mitemxx
{$\Gp{x^2+4x+29}\Gp{3x+1}\Gp{3x-2}$}
%\mitemx
{$\Gp{x^2+2x+3}\Gp{x-2}\Gp{5x+6}$}
\mitemx
{$\Gp{w^2+2w+17}\Gp{5w-2}\ifac{-2}{\sqrt{6}}$}
\end{smenum}
Find all real roots of the polynomials below.
\begin{smenum}
\mitemxx
{$x=-\frac{1}{2},\frac{2}{3},-6$}
%\mitemx
{$z=1,-\frac{3}{4},\frac{4}{3},1+\sqrt{5},1-\sqrt{5}$}
\end{smenum}

\end{document}