\input{preamble}

\title{Section 4.6 --- Euler's Number --- Answer Key}

\begin{document}
\maketitle

\section*{Euler's Number and the Natural Log}
Compute each of the following by hand, using the definition of the natural log.
\begin{smenum}
\mitemxxxxx
{$3$}
{$1$}
{$-1$}
{$\frac{1}{2}$}
{$0.13$}
\end{smenum}
Compute each of the following on your calculator. Round your answer to three decimal places.
\begin{smenum}
\mitemxxxxx
{$20.086$}
{$2.718$}
{$1.649$}
{$0.007$}
{$1.073$}
\mitemxxxxx
{$1.386$}
{$0.470$}
{$-0.693$}
{$-4.605$}
{$0.010$}
\end{smenum}

\section*{Interest Compounded Continuously}
You may wish to reference the formulas for compound interest and interest compounded continuously in solving these problems and the ones in the next section.
$$P(t)=P_0\left(1+\frac{r}{n}\right)^{nt}
\qquad
P(t)=P_0e^{rt}$$
\begin{smenum}
\mitemxxxxx
{\$1557.88}
{\$742.54}
{6.7\%}
{12.51 years}
{11.55 years}
\end{smenum}

\section*{Equivalent Interest Rates}
For each loan below, find the equivalent interest rate if the loan were compounded continuously. Answer as a percent, rounded to two decimal places.
\begin{smenum}
\mitemxxx
{3.92\%}
{6.64\%}
{11.15\%}
\end{smenum}
For each loan below, find the equivalent interest rate if the loan were compounded annually. Answer as a percent, rounded to two decimal places.
\begin{smenum}
\mitemxxx
{9.63\%}
{3.66\%}
{7.36\%}
\end{smenum}
%\clearpage
\noindent Answer each of the questions below.
\begin{senum}
\item
\begin{nmenum}
\mitemxxx
{6.2\%, 6.33\%, 6.31\%}
{6.02\%, 6.13\%, 6.12\%}
{The first one}
\mitemx
{Yes: with an investment, she wants more interest, so she should choose the second one.}
\end{nmenum}
\item
\begin{nmenum}
\mitemxxxx
{5.49\%}
{5.38\%}
{5.36\%}
{5.35\%}
\end{nmenum}
\end{senum}

\section*{Percent Rate of Change}
In the questions below, pay close attention to the tricky wording. (Increases/decreases by some percent each time, vs. increases/decreases at a rate of some percent per time.)
\begin{smenum}
\mitemxxxx
{21 hours}
{138,250}
{\$17 million}
{422 mg}
\end{smenum}
\end{document}