\input{preamble}

\title{Section 6.3 --- Circles}

\begin{document}
\maketitle

\section*{Basic Equation of a Circle}
On a separate sheet of paper, sketch each circles described below.
\begin{smenum}
\mitemxx
{Centered at $(-2,1)$ with radius $4$}
{Centered at $(2,3)$ with radius $1$}
\end{smenum}
Give an equation of each circles described below.
\begin{smenum}
\mitemxx
{Centered at $(3,5)$ with radius $2$}
{Centered at $(-5,-2)$ with radius $6$}
\end{smenum}
Give an equation of the circle shown in each graph below.
\begin{smenum}
\mitemxx
{\CircleFit[2in]{5}{-4}{3}}
{\CircleFit[2in]{-3}{2}{5}}
\end{smenum}
Give the center and radius of the circle described by each equation below.
\begin{smenum}
\mitemxx
{$(x-5)^2+(y+2)^2=49$}
{$(x+6)^2+(y+1)^2=40$}
\end{smenum}
On a separate sheet of graph paper, sketch the graph of each equation below.
\begin{smenum}
\mitemxx
{$(x+2)^2+(y-3)^2=25$}
{$(x+4)^2+(y+2)^2=3$}
\end{smenum}

\section*{Writing Equations of Circles}
Give the equation of each circle described below.
\begin{smenum}
\mitemxx
{Centered at $(4,1)$, through $(8,-4)$}
{Centered at $(2,-1)$, hrough $(-5,-2)$}
\mitemxx
{Diameter has endpoints $(-10,3)$ and $(-4,7)$}
{Diameter has endpoints $(-6,-5)$ and $(-2,2)$}
\mitemxx
{Centered at $(-2,4)$, tangent to $x=5$}
{Centered at $(3,-5)$, tangent to $y=-2$}
\mitemxx
{Centered at $(-5,1)$, tangent to the $x$-axis}
{Centered at $(-4,-3)$, tangent to $y=-\frac{5}{3}x-21$}
\end{smenum}
Give an equation of the circles graphed below.
\begin{smenum}
\mitemxx
{\CircleFit[2in]{2}{-1}{2.23607}}
{\CircleFit[2in]{2}{2}{1.41421}}
\end{smenum}

\section*{Working with Standard Form}
Give an equation of each circle below in standard form.
\begin{smenum}
\mitemxx
{Centered at $(4,-2)$ with radius 3}
{Centered at $(-2,-5)$ through point $(-1,-2)$}
\mitemxx
{Diameter has endpoints $(-2,-1)$ and $(5,3)$}
{Centered at $(2,1)$ and tangent to $y=4$}
\end{smenum}
Rewrite each equation below in center-radius form. If the equation describes a true circle, give its center and radius. If it doesn't, state whether it is the equation of a degenerate circle (single point), or if the equation has no solution.
\begin{smenum}
\maitemxx
{x^2+y^2-4x-6y+9=0}
{x^2+y^2-2x+6y-15=0}
\maitemxx
{4x^2+4y^2-8x+16y+11=0}
{x^2+y^2+10x+9=0}
\maitemxx
{x^2+y^2-6x-10y+34=0}
{x^2+y^2+4x-8y+11=0}
\maitemxx
{x^2+y^2+10x-10y+54=0}
{x^2+y^2-2x+10y+26=0}
\end{smenum}
Rewrite each equation below in center-radius form. Then, graph the circle on a separate sheet of graph paper.
\begin{smenum}
\maitemxx
{x^2+y^2-4y-12=0}
{x^2+y^2+10x+2y+17=0}
\mitemx
{$4x^2+4y^2-8x+28y+17=0$}
\end{smenum}

\end{document}