\input{preamble}

\title{Section 1.3 --- Functions and Relations}

\begin{document}
\maketitle

\section*{Understanding Relations}
Let $R=\{(2,5),(3,7),(-8,-2),(9,1)\}$.  Decide whether each statement below is true.
\begin{smenum}
\mitemxxxx
{$2R5$}
{$-7R8$}
{$7R3$}
{$-8R-2$}
\end{smenum}
Let $S$ be the relation graphed below.  Decide whether each statement below is true.
\begin{cpic}[x=.15in,y=.15in]
\DrawGridSquare
\draw[thick] (-5.9,-.2) -- (-4,-4) -- (0,4) -- (4,-4) -- (5.9,-.2);
\end{cpic}
\begin{smenum}
\mitemxxxx
{$0S4$}
{$-4S4$}
{$3S-2$}
{$4S-4$}
\end{smenum}
Let $T=\Set{(x,y)|x^2+y^2=1}$.  Decide whether each statement below is true.
\begin{smenum}
\mitemxxxx
{$0T1$}
{$-1T0$}
{$-1T-1$}
{$0.6T-0.8$}
\end{smenum}

\section*{Domain and Range of a Relation}
For each relation below, describe the domain and range.
\begin{smenum}
\mitemxx
{$Q=\Set{(2,3),(1,\frac{5}{3}),(-1,{3}{5}),(\frac{11}{8},2)}$}
{$R=\Set{(1,2),(1,3),(1,4),(1,5)}$}
\mitemxx
{$S=\Set{(2,-1),(3,-1),(2,7),(3,9)}$}
{$T=\Set{(11,1),(-2,1),(\pi,1),(2.2,1)}$}
\mitemxxxx
{$U$ is graphed below\\\LittleGraph{\draw[thick] (-1,-1) circle (3);}}
{$V$ is graphed below\\\LittleGraph{\draw [thick,domain=-1:2] plot (\x-1,\x*\x-2);\fill (-2,-1) circle (.2);\fill (1,2) circle (.2);}}
{$W$ is graphed below\\\LittleGraph{\fill (-1,-3) circle (.2); \fill (4,-1) circle (.2); \fill (-2,-2) circle (.2); \fill (-3,2) circle (.2); \draw[thick] (-1,-3) -- (4,-1);\draw[thick] (-2,-2) -- (-3,2);}}
{$Z$ is graphed below\\\LittleGraph{\fill (-3,2) circle (.2); \fill (1,2) circle (.2); \draw[thick] (-3,2) -- (1,2); \draw[thick] (-2,-1) parabola bend (0,-3) (3,1); \fill (-2,-1) circle (.2); \fill (3,1) circle (.2);}}
\end{smenum}

\section*{Identifying Functions}
State whether each relation is a function.  If not, give two pairs that show why not.
\begin{smenum}
\mitemxx
{$Q=\Set{(1,5),(-3,2),(-1,5),(4,4)}$}
{$R=\Set{(2,3),(2,4)(4,4)}$}
\mitemxx
{$S=\Set{(1,1),(2,1),(3,1),(4,1)}$}
{$T=\Set{(-1,-1),(-2,-2),(-1,1),(-2,2)}$}
\mitemxxxx
{$U$ is graphed below\\\LittleGraph{\draw[thick] (0,0) circle (4);}}
{$V$ is graphed below\\\LittleGraph{\draw [thick,domain=-3:3] plot (\x-1,\x*\x-2);}}
{$W$ is graphed below\\\LittleGraph{\draw[thick,domain=-3:3] plot (\x,.25*\x*\x*\x+\x);}}
{$Z$ is graphed below\\\LittleGraph{
\foreach \u in {-1,1} 
    {
		\foreach \v in {-1,1}
		    \draw[thick,domain=2/5.9:5.9] plot (\u*\x,\v*2/\x);
    }
}}
\end{smenum}
For each relation below, give two pairs $(x,y)$ that show that the relation is \emph{not} a function. As a hint, remember that $x^2$ and $(-x)^2$ always give the same (positive) result.
\begin{smenum}
\mitemxx
{$J=\Relat{x^2+y^2=8}$}
{$L=\Relat{x=y^2}$}
\end{smenum}

\section*{Function Notation}
Let $f=\Set{(-2,5),(3,-2),(4,7),(8,9)}$. Find each of the following.
\begin{smenum}
\mitemxxxx
{$f(4)$}
{$f(-2)$}
{$f(9)$}
{$f(3)$}
\end{smenum}
The function $g$ is graphed below. Find each of the following.
\begin{cpic}[x=.2in,y=.2in]
\DrawGridSquare
\draw[thick,domain=-2.9:2,smooth,<-] plot (\x-3,\x*\x/2-3);
\draw[thick] (-1,1) -- (2,-5);
\draw[thick, ->] (4,1) -- (5.9,1);
\foreach \x/\y/\fill in {-1/-1/white,-1/1/white,2/-5/black,4/1/white}
		\filldraw[thick,fill=\fill] (\x,\y) circle (0.2);
\end{cpic}
\begin{smenum}
\mitemxxxx
{$g(-3)$}{$g(-1)$}{$g(1)$}{$g(3)$}
\end{smenum}

\section*{Equations of Functions}
Write each function in relation notation.
\begin{smenum}
\mitemxxx
{$f(x)=2x-5$}
{$g(x)=x^2-7x+12$}
{$h(x)=\dfrac{3x-5}{2x+1}$}
\end{smenum}
Each relation below is a function. Rewrite in function notation. You may need to first solve for $y$.
\begin{smenum}
\mitemxxx
{$R=\Relat{y=x^3-x}$}
{$S=\Relat{2x-5y=10}$}
{$T=\Relat{x^2-y=3}$}
\end{smenum}
Let $k(x)=\dfrac{4x^2+2}{x-7}$. Find each of the following. Give your answer as a fraction.
\begin{smenum}
\mitemxxxx
{$k(2)$}{$k(-3)$}{$k(7)$}{$k(0)$}
\mitemx
{There is one real number not in the implicit domain of $k$. Based on your work above, what is $\dom k$?}
\end{smenum}
\end{document}