\input{preamble}

\title{Section 2.1 --- Monomials and Polynomials}

\begin{document}
\maketitle
\section*{Exponents}
For each expression below:
\begin{clist}
\item Identify the base and the exponent.
\item Rewrite as repeated multiplication.
\item Evaluate by multiplying, then check your answer using the exponent key on your calculator.
\end{clist}
\begin{smenum}
\mitemxxxxx
{$2^3$}
{$3^4$}
{$(-4)^2$}
{$5^3$}
{$(-1)^5$}
\end{smenum}
For each of the expressions below:
\begin{clist}
\item Rewrite using a positive exponent.
\item Evaluate using your rewritten expression, then check your answer using your calculator. Answer as a fraction.
\end{clist}
\begin{smenum}
\mitemxxxxx
{$3^{-2}$}
{$5^{-1}$}
{$\left(\frac{2}{3}\right)^{-3}$}
{$(-4)^{-3}$}
{$\left(-\frac{1}{3}\right)^4$}
\end{smenum}

\section*{Simplifying Monomials}
Simplify each monomial below, applying exponent rules as appropriate.
\begin{smenum}
\mitemxxxx
{$b^2b^3$}
{$2y^2\cdot 5y^3z$}
{$\Gp{3x^2}^3$}
{$\Gp{-\frac{3}{2}x}^4$}
\mitemxxxo
{$\Gp{2x^3}^{4}\Gp{2xy}^2$}
{$\frac{3}{8}x^2y\cdot\frac{4}{9}xy^2$}
{$6hk\cdot 7j^5k\cdot(-2)h^2y$}
\end{smenum}

\section*{Using Polynomial Vocabulary}
For each expression, decide whether it is
\begin{Nmenum}
\mitemxxx
{not a polynomial}
{a monomial}
{a binomial}
\mitemxxo
{a trinomial}
{a polynomial with 4 or more terms}
\end{Nmenum}
\begin{smenum}
\mitemxxxx
{$b+2$}
{$-\dfrac{2}{3}tu$}
{$x^3$}
{$x^2-7xy-y^2$}
\mitemxxxx
{$13$}
{$-0.6xy^2$}
{$\dfrac{4m^2}{n}$}
{$4m-\dfrac{3}{n^2}$}
\mitemxxxx
{$\frac{5}{8}ab$}
{$-0.9n^2p^5$}
{$7r^3-9r^2+r-6$}
{$\dfrac{5}{x^2}$}
\mitemxxxx
{$5.7x^4y$}
{$y^4$}
{$x^2+y^{-3}$}
{$2x+1$}
\end{smenum}
%
For each polynomial below:
\begin{clist}
\item Identify the leading term and leading coefficient, if any.
\item Give the degree of the polynomial.
\item Identify any that are constant, linear, quadratic, or cubic.
\end{clist}
\begin{smenum}
\mitemxxxx
{$6x+8y+3z$}
{$17.3x^2-3x+2.1$}
{$18xy^3$}
{$x^3-4x^2+4x+4$}
\mitemxxxx
{$7k+5$}
{$36$}
{$25-x^2$}
{$2u^2+5u^3-u^7$}
\end{smenum}
%
Give an example of each of the following.
\begin{senum}
\item A quadratic trinomial in one variable.
\item A homogenous cubic polynomial with four terms. (Use $x$ and $y$ as your variables.)
\item A linear binomial in one variable.
\item A cubic binomial in one variable.
\end{senum}

\section*{Polynomial Functions}
Let $f(n)=n^2-8n-3$.  Find:
\begin{smenum}
\mitemxxxx
{$f(2)$}
{$f(-3)$}
{$f(\frac{1}{2})$}
{$f(0)$}
\end{smenum}
Let $g(j)=22j^3+5j^2-16j^4+21-14j$.  Find:
\begin{smenum}
\mitemxxxx
{$g(1)$}
{$g(-2)$}
{$g(\frac{1}{4})$}
{$g(-1)$}
\end{smenum}

\end{document}