\input{preamble}

\title{Section 1.3 --- Functions and Relations --- Answer Key}

\begin{document}
\maketitle

\section{Understanding Relations}
Let $R=\{(2,5),(3,7),(-8,-2),(9,1)\}$.  Decide whether each statement below is true.
\begin{smenum}
\mitemxxxx
{$2R5$ -- true}
{$-7R8$ -- false}
{$7R3$ -- false}
{$-8R-2$ -- true}
\end{smenum}
Let $S$ be the relation graphed below.  Decide whether each statement below is true.
\begin{cpic}[x=.15in,y=.15in]
\DrawGridSquare
\draw[thick] (-5.9,-.2) -- (-4,-4) -- (0,4) -- (4,-4) -- (5.9,-.2);
\end{cpic}
\begin{smenum}
\mitemxxxx
{$0S4$ -- true}
{$-4S4$ -- false}
{$3S-2$ -- true}
{$4S-4$ -- true}
\end{smenum}
Let $T=\bigl\{(x,y)|x^2+y^2=1\bigr\}$.  Decide whether each statement below is true.
\begin{smenum}
\mitemxxxx
{$0T1$ -- true}
{$-1T0$ -- true}
{$-1T-1$ -- false}
{$0.6T-0.8$ -- true}
\end{smenum}

\section{Domain and Range of a Relation}
For each relation below, describe the domain and range.
\begin{smenum}
\mitemxx
{$\dom Q = \Set{-1,1,\frac{11}{8},2}$\\$\rng Q = \Set{\frac{5}{3},2,3,35}$}
{$\dom R=\Set{1}$\\$\rng R = \Set{2,3,4,5}$}
\mitemxx
{$\dom S=\Set{2,3}$\\$\rng S=\Set{-1,7,9}$}
{$\dom T=\Set{-2,2.2,\pi,11}$\\$\rng T=\Set{1}$}
\mitemxx
{$\dom Q=[-4,2]$\\$\rng Q=[-4,2]$}
{$\dom V=[-2,1]$\\$\rng V=[-2,2]$}
\mitemxx
{$\dom W=[-3,-2]\cup [-1,4]$\\$\rng{W}=[-3,2]$}
{$\dom Z=[-3,3]$\\$\rng Z=[-3,1]\cup {2}$}
\end{smenum}

\section{Identifying Functions}
State whether each relation is a function.  If not, give two pairs that show why not.
\begin{smenum}
\mitemxxo
{Function}
{Not a function: $(2,3)$ and $(2,4)$ have $x=2$.}
\mitemxxo
{Function}
{Not a function: $(-1,-1)$ and $(-1,1)$ have $x=-1$.}
\mitemx
{Not a function: $(0,4)$ and $(0,-4)$ have $x=0$. (Other pairs are possible.)}
\mitemxx
{Function}
{Function}
\mitemx
{Not a function: $(2,1)$ and $(2,-1)$ have $x=2$. (Other pairs are possible.)}
\end{smenum}
For each relation below, give two pairs $(x,y)$ that show that the relation is \emph{not} a function. As a hint, remember that $x^2$ and $(-x)^2$ always give the same (positive) result.
\begin{smenum}
\mitemx
{$(2,2)$ and $(2,-2)$ have $x=2$. (Other pairs are possible.)}
\mitemx
{$(1,-1)$ and $(1,1)$ have $x=1$. (Other pairs are possible.)}
\end{smenum}

\section{Function Notation}
Let $f=\Set{(-2,5),(3,-2),(4,7),(8,9)}$. Find each of the following.
\begin{smenum}
\mitemxxxx
{$f(4)=7$}
{$f(-2)=5$}
{$f(9)$ is undefined}
{$f(3)=-2$}
\end{smenum}
The function $g$ is graphed below. Find each of the following.
\begin{cpic}[x=.2in,y=.2in]
\DrawGridSquare
\draw[thick,domain=-2.9:2,smooth,<-] plot (\x-3,\x*\x/2-3);
\draw[thick] (-1,1) -- (2,-5);
\draw[thick, ->] (4,1) -- (5.9,1);
\foreach \x/\y/\fill in {-1/-1/white,-1/1/white,2/-5/black,4/1/white}
		\filldraw[thick,fill=\fill] (\x,\y) circle (0.2);
\end{cpic}
\begin{smenum}
\mitemxxxx
{$g(-3)=-3$}{$g(-1)$ is undefined}{$g(1)=-3$}{$g(3)$ is undefined}
\end{smenum}

\section{Equations of Functions}
Write each function in relation notation.
\begin{smenum}
\mitemxxx
{$f=\Relat{y=2x-5}$}
{$g=\Relat{y=x^2-7x+12}$}
{$h=\Relat{y=\dfrac{3x-5}{2x+1}}$}
\end{smenum}
Each relation below is a function. Rewrite in function notation. You may need to first solve for $y$.
\begin{smenum}
\mitemxxx
{$R(x)=x^3-x$}
{$S(x)=\frac{2}{5}x-2$}
{$T(x)=x^2-3$}
\end{smenum}
Let $k(x)=\dfrac{4x^2+2}{x-7}$. Find each of the following. Give your answer as a fraction.
\begin{smenum}
\mitemxxxx
{$k(2)=-\frac{18}{5}$}{$k(-3)=-\frac{18}{5}$}{$k(7)$ is undefined}{$k(0)=\frac{2}{7}$}
\mitemx
{$\dom k=\Set{x\mid x\neq 7}$}
\end{smenum}
\end{document}