\input{preamble}

\title{Section 3.10 --- Simplifying Radical Expressions --- Answer Key}

\begin{document}
\maketitle

\section{Simplifying Radical Expressions}
Simplify each expression. Do \emph{not} assume variables represent positive real numbers.
\begin{smenum}
\mitemxxxx
{$4\sqrt{6}$}
{$2\sqrt[3]{4}$}
{$2\sqrt[5]{4}$}
{$6\sqrt[4]{3}$}
\mitemxxxx
{$\Abs{x^3y^8z^5}$}
{$\Abs{r^4x^2}\sqrt{rx}$}
{$m^4n^3\sqrt[3]{m}$}
{$3\Abs{x^2}\sqrt[4]{3x}$}
\mitemxxxo
{$2n^3\sqrt[5]{5n^3}$}
{$3x^5\sqrt[3]{18x}$}
{$a^2bc\sqrt[7]{a^2b^2c^5}$}
\end{smenum}

\section{Rationalizing Denominators}
Rationalize each denominator. Assume all variables represent positive real numbers.
\begin{smenum}
\mitemxxx
{$\dfrac{4\sqrt{2x}}{2x^2}$}
{$\dfrac{2x\sqrt[3]{3xy}}{3y}$}
{$\dfrac{2\sqrt{15xy}}{5y^3}$}
\end{smenum}
Rationalize each denominator. Write your answer as a fraction with a positive integer denominator. (If necessary, multiply your numerator and denominator by $-1$.)
\begin{smenum}
\mitemxxx
{$\dfrac{-5-5\sqrt{3}}{2}$}
{$\dfrac{34-3\sqrt{6}}{19}$}
{$\dfrac{3}{2-\sqrt{2}}$}
\mitemxxx
{$\dfrac{7\sqrt{6}-7\sqrt{2}}{4}$}
{$\dfrac{-2+4\sqrt{3}-\sqrt{5}+2\sqrt{15}}{11}$}
{$\dfrac{4\sqrt{5}+4\sqrt{2}}{3}$}
\end{smenum}

\section{Multiple Radical Terms}
Add or subtract.  Simplify your answer as much as possible. Assume all variables represent positive real numbers.
\begin{smenum}
\mitemxxxx
{$12\sqrt{y}$}
{$-y\sqrt{5y}$}
{$5\sqrt[3]{3}$}
{$6\sqrt[4]{2}$}
\mitemxx
{$4n\sqrt[3]{2n}+4m\sqrt[3]{5m}$}
{$\frac{106}{5}\sqrt{5}-12\sqrt{3}$}
\end{smenum}

\section{Write as a Single Radical}
Use rational exponents to simplify each expression by writing it as a single simplified radical.  Assume all variables represent positive real numbers.
\begin{smenum}
\mitemxxxx
{$\sqrt[12]{y^{11}}$}
{$x\sqrt[10]{x^3}$}
{$\sqrt[12]{y^{11}}$}
{$\sqrt[12]{3456}$}
\mitemxxxx
{$\sqrt[6]{n}$}
{$\sqrt[9]{x^8}$}
{$\sqrt[6]{288}$}
{$\sqrt[20]{96}$}
\end{smenum}

\section{Roots in Lowest Terms}
Simplify by writing each expression with the smallest possible index. Assume all variables represent positive real numbers. Give your answer as a simplified radical.
\begin{smenum}
\mitemxxxx
{$\sqrt{x}$}
{$\sqrt[4]{z^3}$}
{$y\sqrt[3]{y}$}
{$w^2\sqrt{w}$}
\mitemxxxx
{$\sqrt{49}$}
{$\sqrt{5}$}
{$2\sqrt{2}$}
{$-\sqrt[3]{3}$}
\end{smenum}

\end{document}