\subsection{Descartes's Rule of Signs} 
How can we predict how many zeros a polynomial will have? We have a theorem to help us that's a little tricky to understand, but easy to apply.
\begin{theorem}[Descartes's Rule of Signs]
For a polynomial $P(x)$ with real coefficients written in descending order, the number of positive real roots is either equal to the number of \emph{sign changes} of the coefficients, or less than that by an even number.

To find number of negative real roots, apply the same rule to $P(-x)$.
\end{theorem}
The proof of this theorem requires techniques we don't have yet, unfortunately, so we won't see it here.

The most important question about this theorem is, what does it mean by a ``sign change''? Consider the polynomial
\[
P(x)=x^3+3x^2-10x-24
\]
\begin{itemize}
\item The coefficients are: $\makeblank[.5in]\quad\makeblank[.5in]\quad\makeblank[.5in]\quad\makeblank[.5in]$
\item \makeblank[.5in] and \makeblank[.5in] are both positive. This is not a sign change.
\item \makeblank[.5in] is positive, but then \makeblank[.5in] is negative. This is a sign change: the \makeblank[1in] goes from positive to negative.
\item \makeblank[.5in] and \makeblank[.5in] are both negative. This is not a sign change.
\item The polynomial has \makeblank[.5in] sign change, so according to the rule it must have \makeblank[.5in] positive real root.
\end{itemize}
What about the negative real roots? For that, we have to work out $P(-x)$. For that, we need to remember two things we know about exponents:
\[
(-x)^n=x^n\mbox{ if $n$ is even}
\qquad
(-x)^n=-x^n\mbox{ if $n$ is odd}
\]
\begin{lpic}{}{2}
\regtextleft{1}{-1}{$P(-x)=$};
\end{lpic}
\begin{itemize}
\item The coefficients are: $\makeblank[.5in]\quad\makeblank[.5in]\quad\makeblank[.5in]\quad\makeblank[.5in]$
\item \makeblank[.5in] is negative, but then \makeblank[.5in] is positive. This is a sign change.
\item \makeblank[.5in] and \makeblank[.5in] are both positive. This is not a sign change.
\item \makeblank[.5in] is positive, but then \makeblank[.5in] is negative. This is a sign change.
\item The polynomial has \makeblank[.5in] sign changes. The polynomial has \makeblank[.5in] or \makeblank[.5in] negative real roots.
\end{itemize}
In fact the roots of this polynomial are $-4$, $-2$, and $3$.