\subsection{Factoring Fully with Rational Roots} 
We now know enough to factor a lot of polynomials that we couldn't in \unref{UnPolyBasics}. Let's see the whole process, for an example that has only rational roots.
\begin{Example}
Factor this polynomial as a product of linear factors.
\[
2x^4-17x^3+68x-32
\]
This polynomial has \makeblank[.5in] terms, so we should try \makeblank
\begin{lpic}{}{3}
\end{lpic}
Grouping failed--but now we have more advanced techniques!

First, we want to know how many zeros we're looking for.
\begin{itemize}
\item The polynomial has \makeblank[.5in] sign changes, so it should have \makeblank[1in] positive roots.
\item Substituting $-x$ gives \makeblank
\item This has \makeblank[.5in] sign changes, so the polynomial should have \makeblank[1in] negative roots.
\end{itemize}

We'll try to find at least one rational root.
\begin{itemize}
\item The factors of \makeblank[.5in] are \makeblank
\item The factors of \makeblank[.5in] are \makeblank
\item The possible rational roots are \makeblank[3in]
\end{itemize}
\begin{cpic}{}{7}
\foreach \y in {0,-4} {
	\synthdiv{-6}{\y}{5};
	\foreach \x/\lbl in {0/2,1/-17,2/0,3/68,4/-32}
		\regtext{-3.5+2*\x}{\y-1}{$\lbl$};
}
\end{cpic}
We've found one factor:
\[
2x^4-17x^3+68x-32=\makeblank[3in]
\]
Now we need to continue to factor \makeblank. This has \makeblank[.5in] terms, so we should try \makeblank again--but that still doesn't work.

Let's look at what happens to the possible rational roots.
\begin{itemize}
\item \makeblank[.5in] is no longer a factor of the constant, so \makeblank[.5in] are no longer possible rational roots.
\item We have also already eliminated \makeblank[.5in]: \makeblank[1in] wasn't a factor of the original polynomial, so it can't be a factor of a factor.
\item But \makeblank[.5in] could happen again, so we have to check.
\end{itemize}
We are trying to factor \makeblank. Possible rational roots are \makeblank.
\begin{cpic}{}{7}
	\foreach \a in {-10,0} {
		\foreach \b in {0,-4} {
			\synthdiv{\a}{\b}{4};
			\foreach \x/\lbl in {0/2,1/-13,2/-26,3/16}
				\regtext{2*\x+2.5+\a}{\b-1}{$\lbl$};
			}
	}
	\draw[dashed] (0,0) -- (0,-7);
\end{cpic}
That gives us two factors!
\[
2x^4-17x^3+68x-32=\makeblank[3in]
\]
The remaining factor has \makeblank[.5in] terms, and it's \makeblank[1in], so we can use the \makeblank[.5in] method.
\begin{cpic}{}{3}
\end{cpic}
We now have linear factors, and we can't factor any further.
\[
2x^4-17x^3+68x-32=\makeblank[3in]
\]
The roots of this polynomial are $x=\makeblank$
\end{Example}