\subsection{Polynomial Notation}
At this point, we need a nice way to write a polynomial. This will be useful, but we need to meet some new notation.
\begin{definition}[Polynomial]
A \term{polynomial} in \term{variable} $x$ of \term{degree} $n$ is an expression in the form
\[
a_n x^n + a_{n-1} x^{n-1} + \cdots + a_1 x + a_0
\]
where each $a_n$ is a number and $a_n\neq 0$.

The numbers $a_n$ are called the \term{coefficients}. The polynomial is said to have \term{integer coefficients} if each $a_0,\dots,a_n$ is an integer, \term{rational coefficients} if each $a_0,\dots,a_n$ is a rational number, and \term{real coefficients} if each $a_0,\dots,a_n$ is a real number.
\end{definition}
This definition doesn't tell us anything we didn't know, but the notation might be hard to read. Have a look at this polynomial:
\[
5x^3-11x^2+\frac{2}{3}x-7
\]
\begin{itemize}
\item In this polynomial, $n=\makeblank[.5in]$, so the degree is \makeblank[.5in].
\item The coefficients are:
\[
a_3=\makeblank[.5in]\qquad
a_2=\makeblank[.5in]\qquad
a_1=\makeblank[.5in]\qquad
a_0=\makeblank[.5in]
\]
\item These coefficients are all \makeblank[1.5in] numbers, so this polynomial has \makeblank[1.5in] coefficients.
\end{itemize}
We can also write a polynomial in a more compact notation.
\begin{definition}[Polynomial]
A polynomial expression in the form
\[
\sum_{k=0}^n {a_k x^k}
\]
where the numbers $a_0,\dots,a_n$ are numbers.
\end{definition}
The symbol $\sum{}$ is the Greek letter \makeblank, and it means to add up whatever comes after it by plugging in various numbers for $k$. This definition means the same thing as the first one.