\section{Factors and Synthetic Division}
Why would anyone want to divide polynomials?

It isn't just to complete the system we started to explore in Unit \unref{UnPolyBasics} when we learned to add, subtract, and multiply polynomials. Ultimately, polynomial division will be an important tool in allowing us to solve problems involving polynomials. Remember that factoring polynomials is an important tool in our arsenal of methods for solving equations!

This section is one of the first times in the course that we do what mathematicians tend to think of as ``real math.'' We will meet a number of \emph{theorems} in this section, and we will \emph{prove} some of them. In the videos which explain proofs, your main job is to understand the logic. After you watch these videos, you should try to put away your notes and re-write the proof on your own. Don't try to memorize it; rather, try to understand the underlying reasoning.

\input{Advanced Polynomials/Factors and Synthetic Division/Remainder Theorem} 
\input{Advanced Polynomials/Factors and Synthetic Division/Introduction} 
\input{Advanced Polynomials/Factors and Synthetic Division/Method} 
\input{Advanced Polynomials/Factors and Synthetic Division/Complications}
\input{Advanced Polynomials/Factors and Synthetic Division/Evaluate}
\input{Advanced Polynomials/Factors and Synthetic Division/Notation}
\input{Advanced Polynomials/Factors and Synthetic Division/Roots Zeros and Factors} 
\input{Advanced Polynomials/Factors and Synthetic Division/The Factor Theorem}
\input{Advanced Polynomials/Factors and Synthetic Division/Applying}
\input{Advanced Polynomials/Factors and Synthetic Division/Multiplicity}
\input{Advanced Polynomials/Factors and Synthetic Division/A Note on Fractions}