\subsection{Properties of Equality} 
\begin{definition}[Equation]
An \term{equation} is a statement that two expressions are equal. It is of the form $$\mbox{expression}=\mbox{expression}$$
The equation is \emph{true} if the two expressions represent the same number.
\begin{itemize}
\item A \term{solution} to an equation is a value(s) of the variable(s) in the equation that makes the equation true.
\item The \term{solution set} of an equation is the set of all solutions of the equation.
\item Two equations are \term{equivalent} if they have the same solution set.
\item To \term{solve} an equation means to find its solution set.
\end{itemize}
\end{definition}
We use equations in several ways.
\begin{itemize}
\item To show equivalent expressions.\makeblankex
\item To define a variable symbol.\makeblankex
\item To describe an unknown quantity.\makeblankex
\end{itemize}
The following properties of equality allow us to get equivalent equations.
\begin{colparts}{2}
\draw (-1,0) rectangle (1,-10);
\draw (-1,-5.5) -- (1,-5.5);
\draw (0,0) -- (0,-5.5);
\foreach \x/\lbl/\lblb/\eqn in {-0.5/Additive/c/X+c=Y+c,0.5/Multiplicative/c\neq 0/c(X)=c(Y)} {
	\regtext{\x}{-1}{\textbf{{\lbl} Property of Equality}};
	\regtextleftblock{\x}{-2}{For any expressions $X$ and $Y$ and any real number $\lblb$, the equations}{0.5\textwidth-0.25in};
	\regtext{\x}{-4}{$X=Y$\quad and\quad$\eqn$};
	\regtextleftblock{\x}{-5}{are equivalent.}{0.5\textwidth-0.25in};
}
\regtext{0}{-6.5}{\textbf{Symmetric Property of Equality}};
\regtextleftblock{0}{-7.5}{For any expressions $X$ and $Y$, the equations}{\textwidth-0.25in};
\regtext{0}{-8.5}{$X=Y$ \quad and\quad$Y=X$};
\regtextleftblock{0}{-9.5}{are equivalent.}{\textwidth-0.25in};

\end{colparts}
